Spatial Reasoning and Statistical Graphics

### 2014-10-11 Paper/Draft1/TestingVisualAptitude.Rnw
Remove preliminary

<<correlations, fig.cap="Scree plot of principle component analysis of performance on the different test batteries.", out.width=".5\\linewidth", fig.height=4.5, fig.width=7.5, comment="|">>=
cor(ans.summary[,c("lineup","card_rot", "fig_class", "folding", "vis_search")])
# using scaled version right now, should be changed to unscaled once the scores are internally scaled.
pca <- prcomp(ans.summary[,c("lineup", "card_rot", "fig_class", "folding", "vis_search")], scale=T)
summary(pca)
screeplot(pca)
@

\begin{figure}[htbp]\centering
\includegraphics[width=0.75\textwidth]{fig-VisReasoningAnalysisCts}
\caption[Visual Aptitude Study Results]{Scatterplots of all test scores compared to participants' scores in the lineup tests. \comment{What is the main message of these plots? Relatively strong positive correlation to all established test scores?}}\label{fig:visualaptitudects}
\end{figure}

@@

\begin{figure}[htbp]\centering
\includegraphics[width=\textwidth]{fig-VisReasoningAnalysisCat}
\caption[Visual Aptitude Study Results]{Preliminary results of categorical variables compared to lineup score.}\label{fig:visualaptitudecat}
\end{figure}

>>>>

<<correlations, fig.cap="Scree plot of principle component analysis of performance on the different test batteries.", out.width=".5\\linewidth", fig.height=4.5, fig.width=7.5, comment="|", warning=F, message=F>>=
cor(ans.summary[,c("lineup","card_rot", "fig_class", "folding", "vis_search")])
# using scaled version right now, should be changed to unscaled once the scores are internally scaled.
pca <- prcomp(ans.summary[,c("lineup", "card_rot", "fig_class", "folding", "vis_search")], scale=T)
summary(pca)
screeplot(pca)
@

\begin{figure}[htbp]\centering
\includegraphics[width=0.75\textwidth]{fig-VisReasoningAnalysisCts}
\caption[Visual Aptitude Study Results]{Scatterplots of all test scores compared to participants' scores in the lineup tests. There is a relatively strong positive correlation between lineup score and scores on visuospatial reasoning tests.}\label{fig:visualaptitudects}
\end{figure}

@@

\begin{figure}[htbp]\centering
\includegraphics[width=\textwidth]{fig-VisReasoningAnalysisCat}
\caption[Visual Aptitude Study Results]{Sample demographic characteristics compared with lineup score.}\label{fig:visualaptitudecat}
\end{figure}
